`r paste(params$species)` biomass trends and figures

### 2019-12-06 analysis/VOCC/3-bioclimatic-trends.Rmd
functionize bioclimatic calculations

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-AR1-spatial" 
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set( fig.width = 9, fig.height = 6.5, #fig.width=11, fig.height=8.5, 
                      #fig.path=paste0("figs/", spp, "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

@@

Save predictions for full spatial grid
```{r}
#fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

if (any(names(maturity) == "adult_density")) {
#if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
  adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  #nd$year <- as.integer(nd$year)
  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(adult_biomass$data$year)) %>% 
    mutate(
      do_mlpl_scaled = (log_do - adult_biomass$data$do_mlpl_mean[1]) /(adult_biomass$data$do_mlpl_sd[1]*2), 
      do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)

@@

  adult_predictions$est_rw_i <- adult_predictions_obj$obj$report()$proj_rw_i
  # test_eta <- adult_predictions_obj$obj$report()$proj_eta
  # test_fe <- adult_predictions_obj$obj$report()$proj_fe
  # 
  # test_diff <- test_eta - test_fe
  # range(adult_predictions$est_rw_i)
  # report <- adult_predictions_obj$obj$report()

  saveRDS(adult_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-bioclimatic-prior-", priors, ".rds"))

  imm_biomass <- readRDS(paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

    nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(imm_biomass$data$year))%>% 
    mutate(do_mlpl_scaled = (log_do - imm_biomass$data$do_mlpl_mean[1]) /(imm_biomass$data$do_mlpl_sd[1]*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)
  #nd$year <- as.numeric(nd$year)

@@

  imm_predictions$est_rw_i <- imm_predictions_obj$obj$report()$proj_rw_i

  saveRDS(imm_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-bioclimatic-prior-", priors, ".rds"))

} else {

    total_biomass <- readRDS(paste0("data/", spp, 
      "/model-total-biomass-", spp, "-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))

    nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
    nd <- nd_all %>% 
      filter(ssid %in% model_ssid) %>%
      filter(year %in% unique(total_biomass$data$year))%>% 
    mutate(do_mlpl_scaled = (log_do - total_biomass$data$do_mlpl_mean) /(total_biomass$data$do_mlpl_sd*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    predictions <- predict(total_biomass, newdata = nd)
    saveRDS(predictions, file = paste0("data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"))
}
```

@@

if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-mature-bioclimatic-prior-", priors, ".rds"
  )) %>% filter(ssid %in% model_ssid))
  try(imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-1n3n4n16-imm-bioclimatic-prior-", priors, ".rds"
  )) %>% filter(ssid %in% model_ssid))

@@

    try(predictions <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-total-bioclimatic-prior-", priors, ".rds"
    )) %>% filter(ssid %in% model_ssid))

    if (!exists("predictions")) {
      paste("Total biomass predictions for this survey are also not available.")
    }
  }
} else {

  try({adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-bioclimatic-prior-", priors, ".rds"
    ))
  })
  try({imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-bioclimatic-prior-", priors, ".rds"
    ))
  })

  # OR bind together predictions from different models
  if (bind_predictions) {
    try({pred1n3 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred4 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred16 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-16-mature-bioclimatic-prior-", priors, ".rds"
      ))
    })

    if (!exists("pred1n3")) pred1n3 <- NULL
    if (!exists("pred16")) pred16 <- NULL
    if (!exists("pred4")) pred4 <- NULL
    adult_predictions <- rbind(pred1n3, pred4, pred16)

    try({pred1n3_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-imm-bioclimatic-prior-", priors, ".rds"
      ))
    })
    try({pred4_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-imm-bioclimatic-prior-", priors, ".rds"))
    })
    try({pred16_imm <- readRDS(paste0("data/", spp,
        "/predictions-", spp, covs, "-16-imm-bioclimatic-prior-", priors, ".rds"))
    })

    if (!exists("pred1n3_imm")) pred1n3_imm <- NULL
    if (!exists("pred16_imm")) pred16_imm <- NULL
    if (!exists("pred4_imm")) pred4_imm <- NULL
    imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm)
  }
  }

@@

      try({predictions <- readRDS(paste0("data/", spp,
        "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"))
      })

      if (!exists("predictions")) {
        try({pred1n3_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-1n3-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({pred4_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-4-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({pred16_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-16-total-bioclimatic-prior-", priors, ".rds"))
        })
        try({
          predictions <- rbind(pred1n3_all, pred4_all, pred16_all)
        })

@@

if (exists("adult_predictions")) {
  # to convert from kg/m2 to kg/hectare multiply by 10000
  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000
  adult_predictions$bioclimatic <- exp(adult_predictions$est - adult_predictions$epsilon_st) * 10000
  imm_predictions$bioclimatic <- exp(imm_predictions$est - imm_predictions$epsilon_st) * 10000

  adult_predictions$total_bio <- imm_predictions$est_exp + adult_predictions$est_exp
  imm_predictions$prop_imm <- 
  imm_predictions$est_exp / (adult_predictions$est_exp + imm_predictions$est_exp)

@@

  predictions <- predictions %>% group_by(X,Y) %>% arrange(year) %>% mutate(lag_epsilon = lag(epsilon_st), bioclimatic = est - epsilon_st + lag_epsilon)

  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .999)
  #max_bio <- round(max(predictions$total_bio))
  max_bio <- signif(max(predictions$est_exp), digits = 2)

@@

  p_adult <- list()
  if(exists("adult_predictions")) {
  for (i in seq_len(length(model_ssid))) {
    p_adult[[i]] <- plot_facet_map(ad_prediction_list[[i]], "est_exp",
      raster_limits = c(0, max_raster),
      # legend_position = "none"
      transform_col = fourth_root_power
    ) +
      labs(fill = "kg/ha") +
      ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
    p_adult[[i]]
  }
  } else {
    for (i in seq_len(length(model_ssid))) {
    p_adult[[i]] <- plot_facet_map(ad_prediction_list[[i]], "est_exp",
      raster_limits = c(0, max_raster),
      # legend_position = "none"
      transform_col = fourth_root_power
    ) +
      labs(fill = "kg/ha") +
      ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
    p_adult[[i]]  
    }
  }
  print(p_adult)
```

@@

  if (!exists("out_total")) {
    if (1 %in% model_ssid) {

      .predictions <- filter(predictions, ssid == 1)
      if(length(unique(.predictions$year))==5) indices <- c(1, 1, 1, 2, 2)
      if(length(unique(.predictions$year))==6) indices <- c(1, 1, 1, 2, 2, 2)
      if(length(unique(.predictions$year))==7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if(length(unique(.predictions$year))==8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (3 %in% model_ssid) {
      .predictions <- filter(predictions, ssid == 3)
      if(length(unique(.predictions$year))==5) indices <- c(1, 1, 1, 2, 2)
      if(length(unique(.predictions$year))==6) indices <- c(1, 1, 1, 2, 2, 2)
      if(length(unique(.predictions$year))==7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if(length(unique(.predictions$year))==8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (4 %in% model_ssid) {

      .predictions <- filter(predictions, ssid == 4)
      if(length(unique(.predictions$year))==5) indices <- c(1, 1, 1, 2, 2)
      if(length(unique(.predictions$year))==6) indices <- c(1, 1, 1, 2, 2, 2)
      if(length(unique(.predictions$year))==7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if(length(unique(.predictions$year))==8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (16 %in% model_ssid) {

      .predictions <- filter(predictions, ssid == 16)
      #unique(.predictions$year)
      if(length(unique(.predictions$year))==5) indices <- c(1, 1, 1, 2, 2)
      if(length(unique(.predictions$year))==6) indices <- c(1, 1, 1, 2, 2, 2)
      if(length(unique(.predictions$year))==7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if(length(unique(.predictions$year))==8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (exists("adult_predictions")) {
            saveRDS(out_mature, file = paste0("data/", spp, "/trends-", 
        spp, covs, "-", ssid_string, "-mature-bioclimatic-priors-", priors, ".rds"))

         } else {
      out_total <- out_mature
      rm(out_mature)
      saveRDS(out_total, file = paste0("data/", spp, "/trends-", 
        spp, covs, "-", ssid_string, "-total-bioclimatic-priors-", priors, ".rds"))
    }
  }
}
```

### Recent biomass with trawl footprint
```{r }
if (!exists("out_mature")) {out_recent <- out_total} else {out_recent <- out_mature}

@@

  current_biomass <- plot_vocc(out_recent,
    fill_col = "est_exp_e",
    fill_label = "Mean\nbiomass (kg/ha)\npost-2010",
    raster_alpha = 1,
    viridis_option = "C",
    vec_aes = NULL,
    transform_col = fourth_root_power
  )
  current_biomass <- current_biomass +
    geom_sf(data = trawl_footprint, aes(geometry = geometry / 1000), colour = "gray", fill = "gray", alpha = 0.2, lwd = 0.25, inherit.aes = FALSE) +
    coord_sf(xlim = c(180, 820), ylim = c(5350, 6050), datum = NULL) +
    xlab("") +
    ylab("") +
    theme(panel.grid.major = element_line(colour = "transparent")) +
    ggtitle(paste("Predicted", species, "density with trawl footprint overlain"))
  current_biomass

```

>>>>

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Pacific Cod" # 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-fixed"  
    # year_cutoff: 2012
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 9, fig.height = 6.5, # fig.width=11, fig.height=8.5,
  # fig.path=paste0("figs/", spp, "/"),
  echo = FALSE, warning = FALSE, message = FALSE
)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

@@

Save predictions for full spatial grid
```{r}
# fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

if (any(names(maturity) == "adult_density")) {
  # if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))

  adult_biomass <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-all--", ssid_string, "-prior-", priors, ".rds"
  ))
  # nd$year <- as.integer(nd$year)

  sort(unique(nd_all$year))
  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(adult_biomass$data$year)) %>%
    mutate(
      do_mlpl_scaled = (log_do - adult_biomass$data$do_mlpl_mean[1]) / (adult_biomass$data$do_mlpl_sd[1] * 2),
      do_mlpl_scaled2 = do_mlpl_scaled^2
    ) %>%
    select(-est, -est_non_rf, -est_rf, -omega_s, -epsilon_st, -zeta_s)
  nd <- na.omit(nd)
  sort(unique(nd$year))

@@

  # write as function
  bioclim_by_year <- function(yr, model_for_prior_year, pred_grid) {
    nd <- pred_grid

    nd_trim <- nd %>% filter(year < yr)
    fake_years <- nd %>%
      mutate(year = year - 2) %>%
      filter(year > 2007) %>%
      filter(year < yr)

    fake <- sort(unique(fake_years$year))
    true <- sort(unique(nd$year))

    if (!identical(fake, true)) "Something is wrong with the pred_grid years."

    prior_years <- predict(model_for_prior_year, newdata = nd_trim, return_tmb_object = FALSE)
    fake_est <- predict(model_for_prior_year, newdata = fake_years, return_tmb_object = FALSE)
    fake_est$year <- fake_est$year + 2

    bioclim_start <- filter(prior_years, year >= yr - 2) %>%
      filter(year <= yr - 1) %>%
      mutate(bioclim = est)
    bioclim_end <- filter(fake_est, year >= yr) %>%
      filter(year <= yr + 1) %>%
      mutate(bioclim = est_non_rf + omega_s)
    bioclim_all <- dplyr::bind_rows(bioclim_start, bioclim_end) %>%
      select(X, Y, year, bioclim)

    bioclim_all
  }

  model_pre_2013 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-past-2013-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(model_pre_2013$data$year))

  bioclim_2013 <- bioclim_by_year(2013, model_pre_2013, nd)
  bioclim_2013 <- rename(bioclim_2013, bioclim_2013 = bioclim)
  glimpse(bioclim_2013)

  model_pre_2015 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-past-2015-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(model_pre_2015$data$year))

  bioclim_2015 <- bioclim_by_year(2015, model_pre_2015, nd)
  bioclim_2015 <- rename(bioclim_2015, bioclim_2015 = bioclim)
  glimpse(bioclim_2015)

  model_pre_2017 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-past-2017-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(model_pre_2017$data$year))

  bioclim_2017 <- bioclim_by_year(2017, model_pre_2017, nd)
  bioclim_2017 <- rename(bioclim_2017, bioclim_2017 = bioclim)
  glimpse(bioclim_2017)

  # for multiyear bioclim
  bioclim_multi_year <- function(yr, model_for_prior_year, pred_grid) {
    nd <- pred_grid
    period2_range <- max(nd$year) - yr + 1

    nd_trim <- nd %>% filter(year < yr)
    fake_years <- nd %>%
      mutate(year = year - 2) %>%
      filter(year > 2007) %>%
      filter(year < yr)

    fake <- sort(unique(fake_years$year))
    true <- sort(unique(model_for_prior_year$data$year))

    if (!identical(fake, true)) "Model years doesn't match filtered pred_grid years."

    prior_years <- predict(model_for_prior_year, newdata = nd_trim, return_tmb_object = FALSE)

    past_predictions <- prior_years %>%
      mutate(past_est = est, bioclim = est) %>%
      select(X, Y, year, past_est, bioclim)

    fake_est <- predict(model_for_prior_year, newdata = fake_years, return_tmb_object = FALSE)
    fake_est$year <- fake_est$year + 2

    bioclim <- filter(fake_est, year >= yr + 2 - 2) %>%
      filter(year <= yr + 2 - 1) %>%
      mutate(bioclim = est_non_rf + omega_s)

    if (period2_range >= 4) {
      fake_minus4 <- nd %>%
        mutate(year = year - 4) %>%
        filter(year > 2007)

      fake <- sort(unique(fake_minus4$year))
      true <- sort(unique(nd_trim$year))

      if (!identical(fake, true)) "Model years doesn't match filtered pred_grid years -4."

      fake_est_minus4 <- predict(model_for_prior_year, newdata = fake_minus4, return_tmb_object = FALSE)
      fake_est_minus4$year <- fake_est_minus4$year + 4
      # sort(unique(fake_est_minus4$year))

      bioclim_4 <- filter(fake_est_minus4, year >= yr + 4 - 2) %>%
        filter(year <= yr + 4 - 1) %>%
        mutate(bioclim = est_non_rf + omega_s)

      bioclim <- dplyr::bind_rows(bioclim, bioclim_4)
    }

    if (period2_range >= 6) {
      fake_minus6 <- nd %>%
        mutate(year = year - 6) %>%
        filter(year > 2007)
      fake <- sort(unique(fake_minus6$year))
      true <- sort(unique(nd_trim$year))

      if (!identical(fake, true)) "Model years doesn't match filtered pred_grid years -6."

      fake_est_minus6 <- predict(model_for_prior_year, newdata = fake_minus6, return_tmb_object = FALSE)
      fake_est_minus6$year <- fake_est_minus6$year + 6

      bioclim_6 <- filter(fake_est_minus6, year >= yr + 6 - 2) %>%
        filter(year <= yr + 6 - 1) %>%
        mutate(bioclim = est_non_rf + omega_s)

      bioclim <- dplyr::bind_rows(bioclim, bioclim_6)
    }

    bioclim_all <- dplyr::bind_rows(past_predictions, bioclim) %>%
      select(X, Y, year, past_est, bioclim)

    bioclim_all
  }

  model_pre_2015 <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-past-2015-", ssid_string, "-prior-", priors, ".rds"
  ))

  bioclim_blob <- bioclim_multi_year(2015, model_pre_2015, nd)
  bioclim_blob <- rename(bioclim_blob, bioclim_blob = bioclim)
  glimpse(bioclim_blob)
  #View(bioclim_blob)

  adult_predictions <- left_join(adult_predictions, bioclim_blob)
  adult_predictions <- left_join(adult_predictions, bioclim_2013)
  adult_predictions <- left_join(adult_predictions, bioclim_2015)
  adult_predictions <- left_join(adult_predictions, bioclim_2017)

  View(adult_predictions)

  saveRDS(adult_predictions, file = paste0(
    "data/", spp,
    "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-mat-2015-cutoff.rds"
  ))

  #################
  #### Immature
  #################

  imm_biomass <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-all--", ssid_string, "-prior-", priors, ".rds"
  ))

  nd <- nd_all %>%
    filter(ssid %in% model_ssid) %>%
    filter(year %in% unique(imm_biomass$data$year)) %>%
    mutate(do_mlpl_scaled = (log_do - imm_biomass$data$do_mlpl_mean[1]) / (imm_biomass$data$do_mlpl_sd[1] * 2), do_mlpl_scaled2 = do_mlpl_scaled^2)
  nd <- na.omit(nd)

@@

  imodel_pre_2013 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-past-2013-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(imodel_pre_2013$data$year))

  bioclim_2013 <- bioclim_by_year(2013, imodel_pre_2013, nd)
  bioclim_2013 <- rename(bioclim_2013, bioclim_2013 = bioclim)
  glimpse(bioclim_2013)

  imodel_pre_2015 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-past-2015-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(imodel_pre_2015$data$year))

  bioclim_2015 <- bioclim_by_year(2015, imodel_pre_2015, nd)
  bioclim_2015 <- rename(bioclim_2015, bioclim_2015 = bioclim)
  glimpse(bioclim_2015)

  imodel_pre_2017 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-past-2017-", ssid_string, "-prior-", priors, ".rds"
  ))
  sort(unique(imodel_pre_2017$data$year))

  bioclim_2017 <- bioclim_by_year(2017, imodel_pre_2017, nd)
  bioclim_2017 <- rename(bioclim_2017, bioclim_2017 = bioclim)
  glimpse(bioclim_2017)

  imodel_pre_2015 <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-past-2015-", ssid_string, "-prior-", priors, ".rds"
  ))

  bioclim_blob <- bioclim_multi_year(2015, imodel_pre_2015, nd)
  bioclim_blob <- rename(bioclim_blob, bioclim_blob = bioclim)
  glimpse(bioclim_blob)
  #View(bioclim_blob)

  imm_predictions <- left_join(imm_predictions, bioclim_blob)
  imm_predictions <- left_join(imm_predictions, bioclim_2013)
  imm_predictions <- left_join(imm_predictions, bioclim_2015)
  imm_predictions <- left_join(imm_predictions, bioclim_2017)

  saveRDS(imm_predictions, file = paste0(
    "data/", spp,
    "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-imm-2015-cutoff.rds"
  ))
} else { # need to add non-split-by-age version
  # total_biomass <- readRDS(paste0("data/", spp,
  #   "/model-total-biomass-", spp, "-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  #
  # nd_all <- readRDS(paste0("data/predicted-DO-new.rds"))
  # nd <- nd_all %>%
  #   filter(ssid %in% model_ssid) %>%
  #   filter(year %in% unique(total_biomass$data$year))%>%
  # mutate(do_mlpl_scaled = (log_do - total_biomass$data$do_mlpl_mean) /(total_biomass$data$do_mlpl_sd*2), do_mlpl_scaled2 = do_mlpl_scaled^2)
  # nd <- na.omit(nd)
  # nd$year <- as.integer(nd$year)
  #
  # predictions <- predict(total_biomass, newdata = nd)
  # saveRDS(predictions, file = paste0("data/", spp,
  #   "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"))
}
```

@@

if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS(paste0(
    "data/", spp,
    "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-mat-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid))
  try(imm_predictions <- readRDS(paste0(
    "data/", spp,
    "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-imm-2015-cutoff.rds"
  )) %>% filter(ssid %in% model_ssid))

@@

    try(predictions <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-1n3n4n16-total-bioclimatic-prior-", priors, ".rds"
    )) %>% filter(ssid %in% model_ssid))

    if (!exists("predictions")) {
      paste("Total biomass predictions for this survey are also not available.")
    }
  }
} else {
  try({
    adult_predictions <- readRDS(paste0(
      "data/", spp,
      "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-mat-2015-cutoff.rds"
    )) %>% filter(ssid %in% model_ssid)
  })
  try({
    imm_predictions <- readRDS(paste0(
      "data/", spp,
      "/bioclimatic-predictions-", spp, covs, "-", ssid_string, "-imm-2015-cutoff.rds"
    )) %>% filter(ssid %in% model_ssid)
  })

@@

    try({
      predictions <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-", ssid_string, "-total-bioclimatic-prior-", priors, ".rds"
      ))
    })

@@

if (exists("adult_predictions")) {
  # to convert from kg/m2 to kg/hectare multiply by 10000
  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000
  adult_predictions$total_bio <- imm_predictions$est_exp + adult_predictions$est_exp

  # check that both dataframes are arranged similarly
  if (adult_predictions[30000, 6] == imm_predictions[30000, 6]) {
    imm_predictions$prop_imm <-
      imm_predictions$est_exp / (adult_predictions$est_exp + imm_predictions$est_exp)
  }

@@

  # predictions <- predictions %>% group_by(X,Y) %>% arrange(year) %>% mutate(lag_epsilon = lag(epsilon_st), bioclimatic = est - epsilon_st + lag_epsilon)
  #
  predictions$total_bio <- exp(predictions$est) * 10000
  max_raster <- quantile(predictions$total_bio, .999)
  # max_bio <- round(max(predictions$total_bio))
  max_bio <- signif(max(predictions$est_exp), digits = 2)

@@

p_adult <- list()
if (exists("adult_predictions")) {
  for (i in seq_len(length(model_ssid))) {
    p_adult[[i]] <- plot_facet_map(ad_prediction_list[[i]], "est_exp",
      raster_limits = c(0, max_raster),
      # legend_position = "none"
      transform_col = fourth_root_power
    ) +
      labs(fill = "kg/ha") +
      ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
    p_adult[[i]]
  }
} else {
  for (i in seq_len(length(model_ssid))) {
    p_adult[[i]] <- plot_facet_map(ad_prediction_list[[i]], "est_exp",
      raster_limits = c(0, max_raster),
      # legend_position = "none"
      transform_col = fourth_root_power
    ) +
      labs(fill = "kg/ha") +
      ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))
    p_adult[[i]]
  }
}
print(p_adult)
```

@@

  if (!exists("out_total")) {
    if (1 %in% model_ssid) {
      .predictions <- filter(predictions, ssid == 1)
      if (length(unique(.predictions$year)) == 5) indices <- c(1, 1, 1, 2, 2)
      if (length(unique(.predictions$year)) == 6) indices <- c(1, 1, 1, 2, 2, 2)
      if (length(unique(.predictions$year)) == 7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if (length(unique(.predictions$year)) == 8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (3 %in% model_ssid) {
      .predictions <- filter(predictions, ssid == 3)
      if (length(unique(.predictions$year)) == 5) indices <- c(1, 1, 1, 2, 2)
      if (length(unique(.predictions$year)) == 6) indices <- c(1, 1, 1, 2, 2, 2)
      if (length(unique(.predictions$year)) == 7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if (length(unique(.predictions$year)) == 8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (4 %in% model_ssid) {
      .predictions <- filter(predictions, ssid == 4)
      if (length(unique(.predictions$year)) == 5) indices <- c(1, 1, 1, 2, 2)
      if (length(unique(.predictions$year)) == 6) indices <- c(1, 1, 1, 2, 2, 2)
      if (length(unique(.predictions$year)) == 7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if (length(unique(.predictions$year)) == 8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (16 %in% model_ssid) {
      .predictions <- filter(predictions, ssid == 16)
      # unique(.predictions$year)
      if (length(unique(.predictions$year)) == 5) indices <- c(1, 1, 1, 2, 2)
      if (length(unique(.predictions$year)) == 6) indices <- c(1, 1, 1, 2, 2, 2)
      if (length(unique(.predictions$year)) == 7) indices <- c(1, 1, 1, 2, 2, 2, 2)
      if (length(unique(.predictions$year)) == 8) indices <- c(1, 1, 1, 1, 2, 2, 2, 2)

@@

    if (exists("adult_predictions")) {
      saveRDS(out_mature, file = paste0(
        "data/", spp, "/trends-",
        spp, covs, "-", ssid_string, "-mature-bioclimatic-priors-", priors, ".rds"
      ))
    } else {
      out_total <- out_mature
      rm(out_mature)
      saveRDS(out_total, file = paste0(
        "data/", spp, "/trends-",
        spp, covs, "-", ssid_string, "-total-bioclimatic-priors-", priors, ".rds"
      ))
    }
  }
}
```

### Recent biomass with trawl footprint
```{r }
if (!exists("out_mature")) {
  out_recent <- out_total
} else {
  out_recent <- out_mature
}

@@

current_biomass <- plot_vocc(out_recent,
  fill_col = "est_exp_e",
  fill_label = "Mean\nbiomass (kg/ha)\npost-2010",
  raster_alpha = 1,
  viridis_option = "C",
  vec_aes = NULL,
  transform_col = fourth_root_power
)
current_biomass <- current_biomass +
  geom_sf(data = trawl_footprint, aes(geometry = geometry / 1000), colour = "gray", fill = "gray", alpha = 0.2, lwd = 0.25, inherit.aes = FALSE) +
  coord_sf(xlim = c(180, 820), ylim = c(5350, 6050), datum = NULL) +
  xlab("") +
  ylab("") +
  theme(panel.grid.major = element_line(colour = "transparent")) +
  ggtitle(paste("Predicted", species, "density with trawl footprint overlain"))
current_biomass
```

## Trends in biomass density
```{r, error=TRUE}
if (exists("out_mature")) {
  data <- out_mature
  biotrend_ad <- plot_vocc(data,
    fill_col = "units_per_decade",
    fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "lightseagreen", # limegreen",
    low_fill = "red", # "deeppink3",# "steel blue 4",
    transform_col = fourth_root_power,
    # raster_limits = c(0, quantile(data$units_per_decade, 0.99999)),
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(as.numeric(adult_predictions[["year"]]))), "-", max(unique(as.numeric(adult_predictions[["year"]])))
  ))
  biotrend_ad
} else {
  biotrend_ad <- plot_vocc(out_total,
    fill_col = "units_per_decade",
    fill_label = "Biomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "greenyellow", # limegreen",
    low_fill = "red", # "steel blue 4",
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(as.numeric(predictions[["year"]]))), "-", max(unique(as.numeric(predictions[["year"]])))
  ))
  biotrend_ad
}
```
